%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Jay Taves} % Your name
\address{151 E Wilson St. Apt. 201 \\ Madison, WI, 53703} % Your address
\address{425 698 8401 \\ jaytaves@gmail.com \\ github.com/jaytaves} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Simulation Based Engineering Lab}{October \osn{2019} -- Present}{Research Assistant}{Madison, WI}
\item Managed development of SynChrono; an open-source C++ library which parallelizes the physics-based simulation engine Chrono, allowing hundreds of vehicles to operate in real-time. 
\item Prototyped and helped implement a re-write of Chrono::Vehicle's off-road terrain algorithm, speeding it up around 60 times and enabling it to scale to arbitrary terrain sizes.
\item Planned development goals and mentored undergraduates who were contributing to the SynChrono project.
\item Wrote and gave talks on several conference papers and posters, gave technical presentations on design and use of SynChrono.
\end{rSubsection}

\begin{rSubsection}{Epic Systems \textnormal{--- Leading vendor of EMR (Electronic Medical Record) software}}{August \osn{2017} -- June \osn{2019}}{Interfaces Developer and Project Manager}{Madison, WI}
\item Developed a new parsing library and several smaller projects for Epic's HL7 pharmacy interfaces.
\item Managed the conversion of Olmsted Medical Center's legacy patient data into Epic as they went live on Epic's EMR on one of the fastest time-lines that Epic has done to date.
\item Managed interface testing and validation for United Regional Health Care System's transition to Epic.
\end{rSubsection}

\begin{rSubsection}{Atomic and Alternative Energies Commission [CEA]}{Summer \osn{2016}}{Fuel Cladding Simulation Intern}{Saclay, France}
\item Modeled the swelling of nuclear reactor fuel cladding in a French fourth generation fast breeder reactor.
\item Created and ran simulations to test different swelling models for the cladding.
\item Summarized simulation findings and results in a French technical report.
\end{rSubsection}

%\begin{rSubsection}{Custom Shoes by 3D Foot Scanning}{Spring \osn{2016}}{Second Year Group Project}{Châtenay-Malabry, France}
%\item Created a mounted camera and projector setup along with a desktop application to scan feet and measure key dimensions of the foot.
%\item Worked closely with a startup to ensure that the setup allowed them to quickly create custom-fitted shoes for their company.
%\end{rSubsection}

%\begin{rSubsection}{Minimization Research with Dr.~Donald Taves}{\osn{2014} -- \osn{2017}}{Research Assistant}{}
%\item Presented a paper on the effectiveness of Minimization at the \osn{2016} Joint Statistical Meetings in Chicago
%\item Assisted in the clinical trials research of a leading fluoride expert, by developing a tool to create sample trial groups.
%\item Currently developing and maintaining a program that shows how dishonest investigators can be prevented from creating unbalanced control and treatment groups for clinical trials.
%\item The code is publicly available online with a demo at https://github.com/JayTaves/Minimization
%\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Zetron, Inc \textnormal{--- develops mission critical emergency dispatch systems}}{Summers \osn{2013 -- 2015}}{Web Developer}{Redmond, WA}
\item Developed a web tool that replaced Zetron's phone-based quoting process, significantly improving the re-seller sales process.
\item The web tool allows Zetron product specialists to create a questionnaire that re-sellers can use to configure a product for sale.
% \item The tool was developed in JavaScript and C$^\#$ to remain fully compatible with Zetron's existing \textsc{sql} back end database and quote creation process.
\end{rSubsection}

%------------------------------------------------

% \begin{rSubsection}{pickAtime \textnormal{--- Online Parent-Teacher Conference Scheduler}}{Summer \osn{2012}}{Software Developer}{Bellevue, WA}
% \item Improved website design working for pickAtime.
% \item Managed expansion and streamlining of new content on the website.
% \item Wrote a published article promoting the benefits of online scheduling for use in schools.

% \end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Wisconsin--Madison} \hfill {\em Expected May \osn{2021}} \\
Masters in Mechanical Engineering \\
Thesis on applications of high-performance computing to physics-based simulation \\
Researcher in the Simulation Based Engineering Lab

{\bf Cornell University} \hfill {\em May \osn{2017}} \\
B.S. in Mechanical Engineering, Minor in Mathematics \\
Physics Undergraduate TA Spring \osn{2015} \\
Courses in Finite Element Analysis, Non-linear Dynamics and Chaos

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{}r @{\hspace{3ex}} p{14cm} }
Programming & High-performance (CUDA, OpenMP, MPI), Web (JavaScript, C$^\#$, HTML), Scientific (C++, \textsc{Matlab}, Python), Database (SQL, Mumps) \\
Management & Project leader for software development of the open-source library SynChrono. Project management for several Epic Systems interface installations \\
Languages & Fluent in French, working knowledge of Spanish
\end{tabular}

\end{rSection}

\end{document}
